Exploratory Analysis Ethan Schilling

### 2025-12-04 Exploratory Analysis Ethan Schilling.Rmd
my analysis

```{r}
TDS_unfilt <- read_csv("RWAR_TDS.csv")
TOC_unfilt <- read_csv("RWAR_TOC.csv")

@@

ggplot(df_TDS, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TDS Value", title = "TDS over Time")

@@

ggplot(df_TOC, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TOC Value", title = "TOC over Time")

>>>>

```{r}

TDS_unfilt <- read_csv("RWAR_TDS.csv")
TOC_unfilt <- read_csv("RWAR_TOC.csv")

@@

TDS_plot <- ggplot(df_TDS, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TDS Value", title = "TDS over Time")

saveRDS(TDS_plot,"TDS_plot.rds")

@@

TOC_plot <- ggplot(df_TOC, aes(x = date, y = value)) +
  geom_line() +
  labs(x = "Date", y = "TOC Value", title = "TOC over Time")

saveRDS(TOC_plot,"TOC_plot.rds")
